\documentclass{article}

% --- NeurIPS Style Emulation for Single-File Compilation ---
\usepackage[letterpaper]{geometry}
\geometry{
  textheight=9in,
  textwidth=5.5in,
  top=1in,
  headheight=12pt,
  headsep=25pt,
  footskip=30pt
}

% Standard PDFLaTeX/LuaLaTeX compatible packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xspace}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{hyperref}

% NeurIPS font settings (Times for main text)
\usepackage{times}

% Custom macros for the checklist
\newcommand{\answerYes}[1][]{\textcolor{blue}{[Yes] #1}}
\newcommand{\answerNo}[1][]{\textcolor{orange}{[No] #1}}
\newcommand{\answerNA}[1][]{\textcolor{gray}{[NA] #1}}

% NeurIPS-like Title Box Formatting
\makeatletter
\def\@maketitle{%
  \vbox{%
    \hsize\textwidth
    \linewidth\hsize
    \vskip 0.1in
    \hrule height 4\p@
    \vskip 0.25in
    \centering
    {\LARGE\bf \@title \par}
    \vskip 0.29in
    \hrule height 1\p@
    \vskip 0.2in
    \begin{tabular}[t]{c}\bf\@author\end{tabular}%
    \vskip 0.3in
  }
}
\makeatother

% NeurIPS Abstract Styling
\renewenvironment{abstract}%
{%
  \centerline{\large\bf Abstract}%
  \vspace{0.5ex}%
  \begin{quote}%
}
{
  \end{quote}%
  \vskip 1ex%
}

\title{F-REGAL: Improving Federated Graph Alignment with Structural Identity and FedSpray Integration}

\author{
  Adrian Rushing \quad Joseph Williams \\
  \texttt{\{ajr0102, jgw0052\}@auburn.edu}
}

\date{}

\begin{document}

\maketitle

\begin{abstract}
Federated Graph Learning (FGL) faces significant hurdles due to data heterogeneity and the ``majority class poisoning'' effect inherent in standard Graph Neural Network (GNN) message passing. While existing methods like FedSpray address class-wise biases through feature-structure encoding, they often lack the fine-grained structural awareness required for precise node-to-node alignment across disjoint silos. In this work, we propose \textbf{F-REGAL}, a hybrid framework that integrates \textbf{REGAL} (RElational Graph ALignment) with \textbf{FedSpray}. F-REGAL leverages structural identity---defined via logarithmic degree binning and $k$-hop neighbor aggregation---and uses xNetMF for cross-network matrix factorization within a privacy-preserving federated setting. By combining FedSpray's knowledge distillation correction mechanism with REGAL's sub-quadratic node matching, our approach enables alignment-aware embeddings that handle millions of nodes while maintaining strict data sovereignty.
\end{abstract}

\input{section/introduction}

\input{section/related_work}

\input{section/methodology}

\input{section/experiment}

\input{section/conclusion}

\bibliographystyle{unsrt}
\begin{thebibliography}{9}
\bibitem{sun2020adaptive}
Wen Sun, Shiyu Lei, Lu Wang, Zhiqiang Liu, and Yan Zhang. 
\newblock Adaptive federated learning and digital twin for industrial internet of things. 
\newblock \textit{IEEE Transactions on Industrial Informatics}, 17(8):5605--5614, 2020.

\bibitem{ramu2022federated}
Swarna Priya Ramu, et al. 
\newblock Federated learning enabled digital twins for smart cities: Concepts, recent advances, and future directions. 
\newblock \textit{Sustainable Cities and Society}, 79:103663, 2022.
\end{thebibliography}

\end{document}